Spectral Experts for Estimating Mixtures of Linear Regressions

### 2013-06-11 doc/icml-presentation/presentation.tex
Started fixing slides

%\usetheme{NLP}
\usepackage{beamerthemesplit}
\usetheme{default}
\useoutertheme{infolines}

@@

\usepackage{algorithm,algorithmic}

\usepackage{tikz}
\usetikzlibrary{calc,positioning,shapes,shadows,arrows}

@@

    \node<2->[style=box,below=0.1cm of gen] {\obj{%
      {\bf Generative Models}
      \begin{itemize}
        \item Gaussian Mixture Models
        \item Hidden Markov Models
        \item Latent Dirichlet Allocation
        \item PCFGs
        \item \dots
      \end{itemize}
      }};
    \node<3->[style=box] (disc) at (6,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/disc.png}\\
      \hfill Discriminative Models
      }};
    \node<4->[style=box,below=0.1cm of disc] (disc-models) {\obj{%
    {\bf Discriminative Models}
      \begin{itemize}
        \item Latent CRFs
        \item Discriminative LDA
        \item Mixture of Experts
        %\item Semi-Latent Topic Models (Wang and Mori, 2009)
        %\item Discriminative Parsers (Liang et.\ al, 2006)
        \item \dots
      \end{itemize}
      }};
    \node<5->[style=box,below=0.1cm of disc-models] {\obj{%
      {\bf Easy to include features and tend to be more accurate.}
    }};

  \end{tikzpicture}

>>>>

%\usetheme{NLP}
\usetheme{boxes}
\useoutertheme{infolines}
\setbeamertemplate{background}[grid][step=10pt]

@@

%\usepackage{algorithm,algorithmic}

\usepackage{tikz}
\usetikzlibrary{calc,positioning,shapes,shadows,arrows,tikzmark}

@@

\begin{frame}
  \frametitle{Latent Variable Models}

  \splitcolumn{%
    \begin{itemize} 
      \item {\bf Generative Models} \tikzmark{gen}
        \uncover<2->{%
        \begin{itemize}
          \item Gaussian Mixture Models
          \item Hidden Markov Models
          \item Latent Dirichlet Allocation
          \item PCFGs
          \item \dots
        \end{itemize}
        }
      \item<3-> {\bf Discriminative Models} \tikzmark{disc}
        \uncover<4->{%
        \begin{itemize}
          \item Mixture of Experts
          \item Latent CRFs
          \item Discriminative LDA
          \item \dots
          \item {\em Easy to include features and tend to be more accurate.}
        \end{itemize}
        }
      \end{itemize}
  }{%
  \begin{tikzpicture}[remember picture, overlay]
    \draw[use as bounding box] (current page.north west) rectangle (current page.south east);
    \point{mark}{(2cm,0)};
    \point{gen}{(pic cs:gen)};
    \point{disc}{(pic cs:disc)};
    \point{a}{((pic cs:gen) -| mark)};
    \point{b}{((pic cs:disc) -| mark)};
    %\node<1-> at (a) {\includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/gen.png}};
    %\node<1-> at (b) {\includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/disc.png}};
  \end{tikzpicture}
  }
